Ontario Graduate Scholarship: Plan of Study

### 2020-04-13 latex/ogs/main.tex
Updated to final draft v2

When a gymnast is performing a swing-up routine on a bar, they do not kick their
feet at specified time intervals. Rather, a more natural human motion is to
smoothly swing their legs based on their current speed and position
\cite{pendulum_length_giant_gymnastics}. In doing so, they are able to generate
enough momentum to perform backflips on the bar. When controlling mechanical
systems, standard practice is to have a robot's actuators track a function of
time. Much like the gymnast, it is often more natural to track a
function of the robot's current speed and position. The recent techniques
of virtual constraints offer this ability and produce realistic, biologically
plausible motion.

Mechanical systems can be constrained in two ways. Holonomic constraints
restrict position (for instance, car tires remain a fixed distance apart), while
nonholonomic constraints restrict velocities (such as how car tires cannot
slide sideways). Previous research has shown that one can enforce holonomic
constraints through a robot's actuators, using the method of "virtual holonomic
constraints" (VHCs) \cite{vhcs_for_el_systems}. VHCs have been used to control
walking robots \cite{stable-walking}, autonomous bicycles \cite{bicycle},
gymnastics robots \cite{xingbo-thesis}, and snake robots \cite{snake-robot}
among others. These VHCs are a special case of virtual nonholonomic constraints
(VNHCs); in my master's thesis \cite{my-thesis} I developed a general theory for
enforcing VNHCs and designed one which injects energy into the gymnastics robot
created by Wang \cite{xingbo-thesis}, thereby enabling it to perform backflips
on a bar.

@@

VNHCs have been studied with applications to human-robot cooperation
\cite{vnhc-human-robot-coop} and walking robots \cite{vnhc-biped-robot}. Horn
\textit{et.al.} \cite{hybrid_zero_dynamics_bipedal_nhvcs} have also examined
properties of VNHCs for general mechanical systems and applied their results to
stabilizing a chosen gait on walking robots. Our approach is novel since we 
assume one has already stabilized a VNHC, and will develop techniques to
transition to a different VNHC while maintaining pre-specified safety
constraints. Doing so should allow one to start at any configuration and chain
together VNHCs to bring the robot ``close enough" to stabilize a desired orbit.

First we will study mathematical conditions under which on can transition
between two VNHCs. These conditions will allow us to create a control algorithm
to switch between motion patterns. After completing this mathematical
formulation, we will test the theory on a gymnastics robot by designing a
gymnastics routine which is performed by transitioning between several different
VNHCS.

Finally, the advancement in mathematics from this research will enable
improvements to control of other robotic systems. The ability to transition
between complex constraints will allow for more natural expressive motion in
many autonomous systems and may become a standard technique for controlling
biologically inspired robots.

>>>>

When a gymnast is performing a swing-up routine on a bar, they do not kick their
feet at specified time intervals. Rather, a more natural human motion is to
smoothly swing their legs based on their current speed and position
\cite{pendulum_length_giant_gymnastics}. In doing so, they are able to generate
enough momentum to perform backflips on the bar. When controlling mechanical
systems, standard practice is to have a robot's actuators track a function of
time. Much like the gymnast, this can produce unnatural motion.  The recent
techniques of virtual constraints offer the ability to track a function of speed
and position to produce realistic, biologically plausible motion.

Mechanical systems can be constrained in two ways. Holonomic constraints
restrict position (for instance, car tires remain a fixed distance apart), while
nonholonomic constraints restrict velocities (such as how car tires cannot
slide sideways). Previous research has shown that one can enforce holonomic
constraints through a robot's actuators, using the method of "virtual holonomic
constraints" (VHCs) \cite{vhcs_for_el_systems}. VHCs have been used to control
walking robots \cite{stable-walking}, autonomous bicycles \cite{bicycle},
gymnastics robots \cite{xingbo-thesis}, and snake robots \cite{snake-robot}
among others. These VHCs are a special case of the more general virtual
nonholonomic constraints (VNHCs); in my master's thesis \cite{my-thesis} I
developed a theory for enforcing VNHCs and designed one which injects energy
into the gymnastics robot created by Wang \cite{xingbo-thesis}, thereby enabling
it to perform backflips on a bar.

@@

VNHCs have been studied with applications to human-robot cooperation
\cite{vnhc-human-robot-coop} and walking robots \cite{vnhc-biped-robot}. Horn
\textit{et.al.} \cite{hybrid_zero_dynamics_bipedal_nhvcs} have also examined
properties of VNHCs for general mechanical systems and applied their results to
stabilizing a chosen gait on walking robots. Our approach is novel since we 
assume one has already stabilized a VNHC, and will develop techniques to
transition to a second one while maintaining certain safety
constraints. Doing so should allow one to start at any configuration and chain
together VNHCs which drive the configuration close enough to a desired orbit for
stabilization.

First we will study mathematical conditions under which one can transition
between two VNHCs. These conditions will allow us to create a control algorithm
to switch between motion patterns. After completing this mathematical
formulation, we will test the theory on a gymnastics robot by designing a
gymnastics routine which is performed solely by transitioning between several different
VNHCS.

The advancements in mathematics from this research will bring improvements to
the control of other autonomous systems. The ability to transition between
complex constraints will allow for more natural expressive motion and may become
a standard technique for controlling biologically inspired robots.
